Flatiron cleaning

### 2021-10-06 Rmd/Report October 2021.Rmd
Update cleaning and add analysis

@@

`r emo::ji("question_mark")`  
Here are all the line that patients received as frontline therapy (Neo or Adj) containing platinum or taxanes should we remove more type of linename?  
<span style="color:red">**Should we include patients who got a single drug as lot/line?**</span> like Carboplatin, Cisplatin, Oxaliplatin, Paclitaxel or Docetaxel by themself as a single drug?  
<span style="color:red">**Should we include patients who received 1 platinum + something not taxane like Gemcitabine or others?**</span>  
<span style="color:red">**Should we exclude patients who received a platinum + Clinical study drug or a taxane + clinical study drug as we don’t know what the clinical study drug is – is it possible that it could include a platinum or taxane based drug?**</span>  
```{r}
# F0017FB3A8828 starts with gemcitabine then have carbo
therapy_line <- therapy_line %>%
  arrange(patientid, episodedate) %>% 
  mutate(remove_linename_other = case_when(
    linenumber_new == 1 &
      str_detect(linename, "platin|taxel")      ~ "keep",
    linenumber_new == 1 &
      !str_detect(linename, "platin|taxel")     ~ "remove",
  )) %>% 
  group_by(patientid) %>% 
  fill(remove_linename_other, .direction = "down") %>% 
  ungroup() %>% 
  filter(remove_linename_other == "keep") %>% 
  select(-remove_linename_other)

therapy_line %>% 
  filter(linenumber_new == 1) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linename) %>% 
  tbl_summary(sort = list(everything() ~ "frequency"))

@@

### step 8: Remove patients with more than 1 line as Neo
We are removing the 34 patients who received multiple Neoadjuvant line.   
`r emo::ji("question_mark")`  
<span style="color:red">**Can you confirm we are doing the good thing by excluding these patients?**</span>  
Here the lines for the 34 patient.
```{r, rows.print = 40}
therapy_line %>% 
  filter(chemotherapy_type == "Neoadjuvant" &
           (linenumber_new == 2 | linenumber_new == 3 | linenumber_new == 4 | linenumber_new == 5)) %>% 
  select(patientid, linename, linenumber, linenumber_new, linestartdate, lineenddate,
         drugname, episodedate, surgerydate, chemotherapy_type) %>%
  arrange(patientid, episodedate) %>% 
  distinct(patientid, linenumber_new, .keep_all = TRUE) %>% 
  select(-linenumber)

>>>>

### step 5: Remove chemotherapy only patients
```{r}
drugs1 <- drugs1 %>%
  filter(!is.na(surgerydate))
drugs1 %>% distinct(patientid) %>% nrow()
```

@@

`r emo::ji("question_mark")`  
Here are all the line that patients received as frontline therapy (Neo or Adj) containing platinum or taxanes should we remove more type of linename?  
<span style="color:red">**Should we include patients who got a single drug as lot/line?**</span> like Carboplatin, Cisplatin, Oxaliplatin, Paclitaxel or Docetaxel by themself as a single drug?  
<span style="color:red">**Should we include patients who received 1 platinum + something not taxane like Gemcitabine or others?**</span> `r emo::ji("no_entry_sign")` <span style="color:green">**Only include single or dual P/T +/- Bev**</span>

```{r}
# F0017FB3A8828 starts with gemcitabine then have carbo
therapy_line1 <- therapy_line %>%
  arrange(patientid, episodedate) %>% 
  mutate(drug_count = sapply(str_split(linename, ","), length)) %>% 
  select(patientid, linename, linenumber, linenumber_new, drug_count, drugname, therapy, treatment_sequence) %>%

  mutate(remove_linename_other = case_when(
    linenumber == 1 &
      # treatment_sequence == "neo + surg + adj" &
      drug_count == 1 &
      str_detect(linename, "platin|taxel")       ~ "keep",
    linenumber == 1 &
      drug_count == 2 &
      (
      (str_detect(linename, "platin") &
      str_detect(linename, "taxel")) |
      (str_detect(linename, "platin") &
      str_detect(linename, "Bev")) |
        (str_detect(linename, "taxel") &
      str_detect(linename, "Bev"))
      )                                           ~ "keep",
    linenumber == 1 &
      drug_count == 3 &
      str_detect(linename, "platin") &
      str_detect(linename, "taxel") &
      str_detect(linename, "Bev")                 ~ "keep",

    TRUE                                          ~ NA_character_,
  )) %>% 
  group_by(patientid) %>% 
  fill(remove_linename_other, .direction = "down") %>% 
  ungroup() %>% 
  filter(remove_linename_other == "keep") %>% 
  select(-remove_linename_other)

therapy_line1 %>% 
  filter(linenumber == 1#, treatment_sequence == "neo + surg + adj"
         ) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linename) %>% 
  tbl_summary(sort = list(everything() ~ "frequency"))

therapy_line1 %>% 
  filter(linenumber == 2, treatment_sequence == "neo + surg + adj") %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linename) %>% 
  tbl_summary(sort = list(everything() ~ "frequency"))

@@

### step 8: Remove patients with more than 1 line as Neo
We are removing the 34 patients who received multiple Neoadjuvant line.   
`r emo::ji("check")`

Here the lines for the 34 patient.
```{r, rows.print = 40}
therapy_line %>% 
  filter(chemotherapy_type == "Neoadjuvant" &
           (linenumber_new == 2 | linenumber_new == 3 | linenumber_new == 4 | linenumber_new == 5)) %>% 
  select(patientid, linename, linenumber, linenumber_new, linestartdate, lineenddate,
         drugname, episodedate, surgerydate, chemotherapy_type) %>%
  arrange(patientid, episodedate) %>% 
  distinct(patientid, linenumber_new, .keep_all = TRUE) %>% 
  select(-linenumber)
